New insights into the Weddell Sea ecosystem applying a network approach

### 2022-11-01 Manuscript/Manuscript.Rmd
Updating Results

The so-called 'High IS' and 'Low IS' groups of species exhibited different and, in some cases, opposite relationships with unweighted properties. It's noteworthy that only the relationship with trophic level revealed a similar trend in the regression analysis for both groups: mean interaction strength increases with trophic level (Figure 5A). On the contrary, the linear regressions with degree and trophic similarity showed opposite relationships comparing groups. These mean that in species with relatively higher mean interaction strength, 'High IS', such strength decreases when the number of interactions (degree) increases; the opposite occurs in species with relatively lower interaction strength 'Low IS' (Figure 5B). Regarding trophic similarity, the interaction strength decreases in 'High IS' species while increases in 'Low IS' species (Figure 5C).

>>>>

CONTINUE MODIFYING HERE:
The so-called 'High IS' and 'Low IS' groups of species exhibited different and, in some cases, opposite relationships with unweighted properties. It's noteworthy that only the relationship with trophic level revealed a similar trend in the regression analysis for both groups: mean interaction strength increases with trophic level (Figure 5A). On the contrary, the linear regressions with degree and trophic similarity showed opposite relationships comparing groups. These mean that in species with relatively higher mean interaction strength, 'High IS', such strength decreases when the number of interactions (degree) increases; the opposite occurs in species with relatively lower interaction strength 'Low IS' (Figure 5B). Regarding trophic similarity, the interaction strength decreases in 'High IS' species while increases in 'Low IS' species (Figure 5C).
